Scikit-learn: machine learning without learning the machinery

### 2014-05-19 article.tex
minted -> listings
Needs tweaking (font too big)

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
%\usepackage{dblfloatfix}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

\definecolor{rulecolor}{rgb}{0.80,0.80,0.80}
\newminted{python}{frame=single,rulecolor=\color{rulecolor}}

@@

\begin{document}

@@

% XXX make_pipeline is not in 0.14.1, we should release 0.15 sometime
% The example can be made a bit shorter by skipping the movie_reviews dir;
% the tarball from Pang et al. contain top-level cruft.
\begin{pythoncode}
import os.path
import tarfile
from urllib import urlretrieve
from sklearn.datasets import load\_files
from sklearn.feature\_extraction.text import TfidfVectorizer
from sklearn.linear\_models import LogisticRegression
from sklearn.pipeline import make\_pipeline

temp, \_ = urlretrieve('http://preview.tinyurl.com/review-tgz')
with tarfile.open(temp) as tar:
    tar.extractall(path='movie\_reviews')
data = load\_files(os.path.join('movie\_reviews', 'txt\_sentoken'))

clf = make\_pipeline(TfidfVectorizer(min\_df=2, dtype=float,
                                    sublinear\_tf=True, ngram\_range=(1, 2),
                                    strip\_accents='unicode'),
                     LogisticRegression(random\_state=623, C=5000))
clf.fit(data.data, data.target)
\end{pythoncode}

@@

\begin{pythoncode}
>>> clf.predict\_proba(["This movie is the worst I ever saw.",
...                    "Shawshank Redemption, eat your heart out!"])
array([[  9.99293000e-01,   7.07000280e-04],
       [  1.68757754e-01,   8.31242246e-01]])
\end{pythoncode}

@@

\begin{pythoncode}
>>> from sklearn.cross\_validation import cross\_val\_score
>>> score = cross\_val\_score(clf, data.data, data.target, cv=5)
>>> score
array([ 0.91  ,  0.8825,  0.88  ,  0.8775,  0.86  ])
>>> score.mean()
0.88200000000000001
\end{pythoncode}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
%\usepackage{dblfloatfix}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

@@

\begin{document}
\lstset{language=Python}

@@

% XXX make_pipeline is not in 0.14.1, we should release 0.15 sometime
% The example can be made a bit shorter by skipping the movie_reviews dir;
% the tarball from Pang et al. contain top-level cruft.
\begin{lstlisting}
import os.path
import tarfile
from urllib import urlretrieve
from sklearn.datasets import load_files
from sklearn.feature_extraction.text import TfidfVectorizer
from sklearn.linear_models import LogisticRegression
from sklearn.pipeline import make_pipeline

temp, _ = urlretrieve('http://preview.tinyurl.com/review-tgz')
with tarfile.open(temp) as tar:
    tar.extractall(path='movie_reviews')
data = load_files(os.path.join('movie_reviews', 'txt_sentoken'))

clf = make_pipeline(TfidfVectorizer(min_df=2, dtype=float,
                                    sublinear_tf=True, ngram_range=(1, 2),
                                    strip_accents='unicode'),
                     LogisticRegression(random_state=623, C=5000))
clf.fit(data.data, data.target)
\end{lstlisting}

@@

\begin{lstlisting}
>>> clf.predict_proba(["This movie is the worst I ever saw.",
...                    "Shawshank Redemption, eat your heart out!"])
array([[  9.99293000e-01,   7.07000280e-04],
       [  1.68757754e-01,   8.31242246e-01]])
\end{lstlisting}

@@

\begin{lstlisting}
>>> from sklearn.cross_validation import cross_val_score
>>> score = cross_val_score(clf, data.data, data.target, cv=5)
>>> score
array([ 0.91  ,  0.8825,  0.88  ,  0.8775,  0.86  ])
>>> score.mean()
0.88200000000000001
\end{lstlisting}
